A Large-Scale Study of the Use of Eval in R

### 2020-08-21 inst/paper/main.tex
abstract

\renewcommand{\c}[1]{{\small\sf{#1}}\xspace}

\begin{abstract}
  The eval function turns text into code and thus causes difficulties for
  reasoning about the behavior of software that uses it. This paper is a
  study of the usage of eval in R, a widely used data science programming
  language. We combine static and dynamic analysis on a large and
  representative corpus of R programs. Our results show...
\end{abstract}

@@

There is some work on

\section{Shade of Eval}

>>>>

\renewcommand{\c}[1]{{\texttt{#1}}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}

\begin{abstract}
  The \c{eval} function turns text into code. The widespread use of that
  capability hinders the static reasoning about software systems. This paper
  is a large-scale study of a corpus of \miss{3} million lines of R code.
  We performed static and dynamic analysis of our corpus and report that
  usage of \c{eval} is indeed wide spread. It is used by expert core
  developers of the language, experienced library developers, and end-users
  alike. The patterns of usage range from meta-programming to
  misunderstandings of what \c{eval} is good for. Case studies give example
  use-cases and some evidence that automated tools could be used to refactor
  some of the uses of \c{eval}.
\end{abstract}

@@

Othere languages

Dynamic analysis

\section{Shades of Eval}
